Describing the C-space of asynchronous periodic task using DIT

### 2013-07-22 dit-paper_ieee.tex
indent fix

  Mathematically,
  \[
    \dbf{t_1, t_2} = \sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i
  \]
  where $n_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and
  deadline both are in the interval $[t_1, t_2]$.\\

@@

\begin{theorem}
\[
  \begin{array}{c}
    (\tau_1, ..., \tau_n) \: \text{is feasible}  \iff \\
    \dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
  \end{array}
\]
\end{theorem}

@@

  \subsubsection{Description using DBF}

  \label{sct:cspaceDescr}

@@

  \subsection{Existence condition}

As in the synchronous case, the problem of existence of the first periodic DIT can be written as a system of modular equation:
$$
\begin{array}{l}
  \exists ? \; t_d \; s.t. \; \forall i \; :\\
  \left\{
    \begin{array}{l}
    t_d > O_i \\
    t_d - O_i \equiv a_i \; (mod \; T_i) \\
    a_i \in [D_i, T_i]
  \end{array}
\right.
\end{array}
$$

This system is guaranteed to have at least one solution modulo $H$ for given values of $a_i$ if the following condition is respected $$a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i, j$$

>>>>

	Mathematically,
	\[
		\dbf{t_1, t_2} = \sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i
	\]
	where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
	and deadlines are both in the closed interval $[t_1, t_2]$.\\

@@

	\begin{theorem}
	\[
		\begin{array}{c}
			\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
			\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{array}
	\]
	\end{theorem}

@@

		\subsubsection{Description using DBF}
			\label{sct:cspaceDescr}

@@

\subsection{Existence condition}
	As in the synchronous case, the problem of existence of the first periodic DIT
	can be written as a system of modular equations:
	\[
		\begin{array}{l}
			\exists ? \; t_d \; s.t. \; \forall i \; :\\
			\left\{
				\begin{array}{l}
					t_d > O_i \\
					t_d - O_i \equiv a_i \; (mod \; T_i) \\
					a_i \in [D_i, T_i]
				\end{array}
			\right.
		\end{array}
	\]

	This system is guaranteed to have at least one solution modulo $H$ for given
	values of $a_i$ if the following condition is respected :
	\[
		a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
		T_j)) \; \forall i,j
	\]
